\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsthm,textcomp}
\usepackage{mathtools}
\usepackage{biblatex}
\usepackage{tikz}
\usepackage{graphics, setspace}
\usepackage{listings}
\usepackage{lipsum}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
\DeclareMathOperator{\Ima}{Im}
\newcommand{\Ba}{\mathcal{B}}
\newcommand{\Ta}{\mathcal{T}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\p}{\mathbb{P}}
\newcommand{\Ss}{\mathcal{S}} % Schwartz space
\newcommand{\F}{\mathcal{F}} % Fourier Transform
\newcommand{\Rf}{\mathcal{R}} % reflection
\newcommand{\E}{\mathbb{E}}
\newcommand{\Int}{\text{Int }}
\newcommand{\Bd}{\text{Bd }}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
% Swap the definition of \abs* and \norm*, so that \abs
% and \norm resizes the size of the brackets, and the 
% starred version does not.
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
%
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

\renewcommand{\theenumi}{\alph{enumi}}
\renewcommand{\labelenumii}{\roman{enumii}.}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem*{definition}{Definition}
\newtheorem*{remark}{Remark}

\theoremstyle{remark}
\newtheorem*{sol}{Solution}

\newenvironment{ex}[1]
    {\noindent\textbf{Exercise #1}\normalsize\newline}
    {\vspace{0.5 em}}

\title{Topology - X400416}
\author{Yoav Eshel}
\date{\today}

\setcounter{secnumdepth}{1}

\begin{document}
\maketitle
\tableofcontents
\newpage

These notes are based on Topology ($2^\text{nd}$ edition) by James R. Munkres. 
\section{Summary}
% write down a summary of important definition/theorems as well as useful techniques for solving exercises
\section{Topological Spaces}
The motivation behind defining a topological space is to generalize the notion of a metric space.
Recall that a metric on a set $X$ is a map $d:X\times X \to [0,\infty)$ that satisfies
\begin{enumerate}
    \item $d(x,y)=d(y,x)$
    \item $d(x,x)=0$
    \item $d(x,y)>0, x\not=y$
    \item $d(x,y)\leq d(x,z)+d(z,y)$
\end{enumerate}
Then we say that a set $U\subset X$ is open if for all $x\in U$ and some $r>0$ 
$$
    B(x,r):=\{y\in X\mid d(x,y)<r\}\subset U.
$$
In other words, around every point in $U$ there is a "ball" that is contained in $U$. 
In Analysis I one learns about continuity using the classic $\varepsilon$-$\delta$ definition which requires a metric.
As it turns out, we don't really need a metric to define a continuous function, only open sets:
\begin{definition}
    A function between metric spaces is continuous if and only if the preimage of an open set is open.
\end{definition}
Using this definition, different seeming metric can yield the same notions of which functions are continuous! 
We call the collection of open subsets of $X$ defined by some metric $d:X\times X\to [0,\infty)$ a \textbf{topology}.
This open sets satisfy some important properties. Namely: (1) $X$ and $\varnothing$ are open, (2) arbitrary unions of open sets are open and (3) finite intersections of open sets is open.
It turns out that a metric is not required to define a topology, only these three properties:
\begin{definition}
    Let $X$ be a set. Then a topology on $X$ is a set $\mathcal{T}\subset\mathcal{P}(x)$ such that
    \begin{enumerate}
        \item $\varnothing\in\Ta, X\in\Ta$
        \item If $\{U_{\alpha}\}\subset\Ta$ then  $\bigcup_{\alpha}U_{\alpha}\in\Ta$
        \item If $\{U_i\}_{i=0}^n\subset\Ta$ then $\bigcap_{i=0}^n U_i\in\Ta$
    \end{enumerate}
    A topological space is the pair $(X,\Ta)$
\end{definition}
Then we say that $U\subset X$ is open if $U\in\Ta$. 
Note that which sets are open depends on the topology, which might conflict with your notion of open set as defined above. 
For example, in the topology $\mathcal{P}(\R)$ every subset of the real line is open, while in the topology $\{\varnothing, \R\}$ only the empty set and $\R$ are open.
We often say that $U$ is open in $X$ without giving a specific topology, which simply means that the statement that follows will hold for any topology we define on $X$ and any element in that topology.

If $\Ta$ and $\Ta'$ are two topologies on $X$ such that $\Ta\subseteq\Ta'$ than we say that $\Ta'$ is \textbf{finer} (or \textbf{strictly finer} if the containment is proper) than $\Ta$. 
We similarly say that $\Ta$ is \textbf{coarser} (or \textbf{strictly coarser}) than $\Ta'$.
It might also be that case that two topologies are not \textbf{comparable}.

\section{Basis for a Topology}
Specifying topologies directly is often not possible, due the enormous size of many topologies.
So we often define a topology using a smaller subset called a \textbf{basis}.
\begin{definition}
    If $X$ is a set, then a \textbf{basis} of a topology is a collection $\mathcal{B}$ of subsets of $X$ such that
    \begin{enumerate}
        \item $\forall x\in X, \exists B\in\mathcal{B}$ such that $x\in B$
        \item If $x\in B_1\cap B_2$ with $B_1,B_2\in\mathcal{B}$ then there exists $B_3\in\mathcal{B}$ with $x\in B_3\subset B_1\cap B_2$.
    \end{enumerate}
\end{definition}
If $\Ta$ is a topology generated by a basis $\Ba$ then $U$ is open if for all $x\in U$ there exists $B\in\Ba$ such that $x\in B\subset U$. 
Also $B\in\Ta$ for all $B\in\Ba$. The proof that $\Ta$ is indeed a topology is not included.
An alternative construction of a topology from a basis is given by the following lemma
\begin{lemma}
    Let $X$ be a set and $\Ba$ a basis for a topology $\Ta$. Then $\Ta$ equals the collection of all unions of elements in $\Ba$.
\end{lemma}
Using this lemma is sometime easier in practice; given a basis $\Ba$ and $U\subset X$, if one can write $U$ as a union of elements in $\Ba$ then $U$ is open.

We can also go in the reverse direction: from topology to a basis.
\begin{lemma}
    Let $X$ be a topological space. If $\mathcal{C}$ is a collection of open sets such that for each open set $U$ and each $x\in U$ there is $C\in\mathcal{C}$ such that $x\in C\subset U$, then $\mathcal{C}$ is a basis.
\end{lemma}

When topologies are given in terms of basis, we can already determine which one is finer using the following criterion
\begin{lemma}
    Let $\Ba$ and $\Ba'$ be bases for the topologies $\Ta$ and $\Ta'$ respectively. Then
    $\Ta\subset\Ta'$ if and only if for each $x\in X$ and $B\in\Ba$ containing $x$ there exists $B'\in\Ba'$ such that $x\in B'\subset B$.
\end{lemma}
It might be tricky to remember the direction of the inclusion. One way to think about it is since $\Ta'$ has more subsets of $X$ it needs to have smaller basis elements.

Lastly, we define the notion of a \textbf{subbasis}.
\begin{definition}
    A subbasis $\Ss$ for a topology on $X$ is a collection of subsets of $X$ whose union equals $X$. The topology generated by $\Ss$ is the collection of all unions of finite intersection of elements of $\Ss$.
\end{definition}

To conclude this section we define 3 topologies on the real line using the notion of a basis:
\begin{enumerate}
    \item The \textbf{standard topology} generated by the collection of all open intervals $(a,b)$ with $a<b$ (it is not a recursive definition. Here we use open in the familiar metric sense).
    \item The \textbf{lower limit topology} is generated by half-open intervals $[a,b)$. When $\R$ is given in the lower limit topology we denote it $\R_l$.
    \item The \textbf{K-topology} is generate by open intervals and sets of the form $(a,b)-K$ where $K=\{1/n\mid n\in\N\}$. When $\R$ is given in this topology we denote it $\R_k$.
\end{enumerate}
One maybe surprising property is that both $\R_l$ and $\R_k$ are finer than the standard topology, but are not comparable with one another.

\section{The Product Topology on $X\times Y$}\label{sec:XtimesY}
Let $X$ and $Y$ be topological spaces. 
The product topology on $X\times Y$ is generated by the collection $\Ba$ of all sets of the form $U\times V$ with $U$ open in $X$ and $V$ open in $Y$.
Alternatively, if $\Ba$ is a basis for $X$ and $\mathcal{C}$ is a basis for $Y$, then
$$
    \mathcal{D}=\{B\times C\mid B\in\Ba, C\in\mathcal{C}\}
$$
is a basis for $X\times Y$.

\section{The Subspace Topology}
If $X$ is a topological space with topology $\Ta_x$ and $Y\subset X$ then the subspace topology on $Y$ is defined as
$$
    \Ta_Y=\{Y\cap U\mid U\in\Ta_X\}.
$$
The fact that the collection $\Ta_Y$ has all the properties of a topology follows from the $\Ta_X$ being a topology.
Then if $\Ba_X$ is a basis for a topology on $X$, the basis of the subspace topology on $Y$ is given by
$$
    \Ba_Y=\{Y\cap B\mid B\in\Ba_X\}.
$$

Open sets in the subspace topology on $Y$ are not necessarily open in $X$.
If $A$ is an open set in $Y$, then $A$ is open in $X$ if $Y$ is open in $X$.

Another fun property of subspace topology is that it "commutes" with the product topology:
If $A$ is a subspace of $X$ and $B$ is a subspace of $Y$ then the product topology on $A\times B$ is equal to the subspace topology on $A\times B$ as a subspace of $X\times Y$.

\section{Closed Sets and Limit Points}
If $X$ is a topological space and $A\subset X$ then $A$ is closed if $X-A$ is open.
Closed sets have similar properties to open sets:
\begin{theorem}
    Let $X$ be a topological space. Then
    \begin{enumerate}
        \item $X$ and $\varnothing$ are closed
        \item Arbitrary intersections of closed sets are close
        \item Finite unions of closed sets are closed.
    \end{enumerate}
\end{theorem}
One can just as well define a topology in terms of closed sets, but the definition using open sets is much more common.
Of course, mathematics wouldn't be fun if there wasn't any space for confusion. In a topology, a set can be open, closed, neither or both. 
So don't think of sets as doors. 

If $Y$ is a subspace of a topological space $X$, then a closed set in $X$ is not necessarily closed in $Y$.
A set $A$ is closed in $Y$ if and only if it equals the intersection of a closed set of $X$ with $Y$. 
This is easy to verify since if $A$ is closed in $Y$ then $Y-A$ is open in $Y$ and so it equals $U\cap Y$ for some open set $U$ in $X$. 
Then $X-U$ is closed and $A=Y\cap(X-U)$. The other direction is similarly proved.

Let $A\subset X$. Then the smallest closed set that contain $A$ is called the closure of $A$ and is denoted 
$$\bar{A}=\bigcap_{\substack{C\text{ closed}\\A\subset C}} C.$$
The smallest open set containing $A$ is called the interior of $A$ and is denoted 
$$\text{Int} A = \bigcup_{\substack{U\text{ open}\\U\subset A}}U.$$ 
Then clearly
$$
    \text{Int}A\subset A\subset\bar{A}.
$$
A point $x\in X$ is in the closure of $A$ if and only if for any basis element $B$ containing $x$ the intersection $A\cap B$ is non empty.

To add to the soup of metaphors, we define the \textbf{neighborhood} of $x\in X$ is an open set $U$ containing $x$. Then a \textbf{limit point} of $A\subset X$ is defined as
\begin{definition}
    A limit point of $A\subset X$ is a point $x\in A$ such that every neighborhood of $x$ intersects $A$ in a point different than $x$
\end{definition}
In other words, $x$ is a limit point of $A$ if for every open set $U$ containing $x$ the intersection $U\cap(A-{x})$ is non empty. Now denote the set of limit points of $A$ by $A'$.
Then $\bar{A}=A'\cup A$. This gives us an alternative condition for a set being closed. Namely, if $A'\subset A$ then $\bar{A}=A$ and so $A$ is closed.
Alternatively, if $A$ is closed, then $\bar{A}=A$ and so $A'\subset A$.
Hence a set is closed if and only if it contains all of its limit points.

We conclude this section with a definition of convergence in a topological space.
\begin{definition}
    Let $(X,\Ta)$ be a topological space. If $x_n$ is a sequence in $X$ then $x_n\to x$ as $n\to\infty$ if
    $$
        \forall U\in\Ta, x\in U\,\exists N\in\N: \{x_n\}_{n\geq N}\subset U
    $$
\end{definition}
Note that this definition does not require any metric. The downside is that limit are not necessarily unique and sequences can converge to any number of points.
To avoid this horrific phenomenon, we add an extra condition to rid our definition of topological spaces of such situations. 
\begin{definition}
    A topological space $X$ is called \textbf{Hausdorff space} if for every $x_1,x_2\in X, x_1\neq x_2$ there exists disjoint neighborhoods $U_1$ and $U_2$ that contain $x_1$ and $x_2$ respectively.
\end{definition}
In essence, this means that we can distinguish between every two points in our topology. Limits of sequences in Hausdorff spaces are unique, which is quiet pleasant.

\section{Continuous Functions}
Recall from the introduction that we defined a function $f:X\to Y$ to be continuous if for each open set $V$ in $Y$ the set
$$f^{-1}(V)=\{x\in X\mid f(x)\in V\} $$
is open in $X$. To prove continuity it suffices to show that for any basis element (or even any subbasis element!) $B\subset Y$, $f^{-1}(B)$ is open in $X$. 
Using this definition, a given function may or may not be continuous depending on the topologies specified for its domain and range. 
If we wish to emphasize it we can say that $f$ is continuous relative to specific topologies.
To illustrate this point, let $\R$ denote the standard topology on the real line and let
$$
    f:\R\to\R_l\quad\text{and}\quad g:\R_l\to\R
$$
be the identity maps, i.e. $x=f(x)=g(x)$ for all $x\in\R$.
Then $f$ is not continuous since $f^{-1}\left([a,b)\right)=[a,b)$ which is not open in the standard topology.
However $g$ is continuous since $g^{-1}\left((a,b)\right)=(a,b)$ which is open in $\R_l$.

There are other equivalent conditions for a function to be continuous
\begin{theorem}
    Let $X$ and $Y$ be topological spaces and $f:X\to Y$. The the following are equivalent
    \begin{enumerate}
        \item $f$ is continuous
        \item For every subset $A$ of $X$ it holds that $f\left(\overline{A}\right)\subset\overline{f(A)}$
        \item For every closed subset $B$ of $Y$, the set $f^{-1}(B)$ is closed in $X$.
        \item For each $x\in X$ and each neighborhood $V$ of $f(x)$ there is a neighborhood $U$ of $x$ such that $f(U)\subset V$.
    \end{enumerate}
\end{theorem}

A bijection $f:X\to Y$ is called a \textbf{homeomorphism} (the e is not a typo. It is indeed a different word to homomorphism!) is both $f$ and $f^{-1}$ are continuous.
An isomorphism in algebra is a bijective map that preserve algebraic structure (between groups, rings, fields, etc.).
In topology, a homeomorphism is a bijective map that preserve topological structure. However in algebra any homomorphism (without an e) that is one-to-one and onto is an isomorphism.
This is, in general, not true in topology. There are continuous bijective maps whose inverses are not continuous. 
If $f:X\to Y$ is injective continuous map, and $g:X\to f(X)$ obtained by restricting the range of $f$ is a homeomorphism, then we say that $f$ is an \textbf{imbedding}.

There are a few important rules for constructing continuous functions
\begin{enumerate}
    \item Constant mappings are continuous
    \item Inclusion mappings are continuous (i.e. if $A$ is a subspace of $X$ and $i:A\to X$ is the identity then $i$ is continuous)
    \item Composition of continuous maps are continuous
    \item Continuous maps restricted to a subspace of their domain are continuous
    \item Restricting or expanding the range of continuous maps gives continuous maps
    \item The map $f:X\to Y$ is continuous if $X$ can be written as the union of open sets $U_\alpha$ such that $f\mid_{U_\alpha}$ is continuous for each $\alpha$
\end{enumerate}

\begin{lemma}{(The pasting lemma)}
    Let $X=A\cup B$ be a topological space and $A, B$ are closed. Consider
    $$ f:A\to Y\quad\text{and}\quad g:B\to Y$$
    continuous such that $f(x)=g(x)$ for all $x\in A\cap B$. Then $h:X\to X$ defined by
    $$ h(x)=\begin{cases}
        f(x),&x\in A\\
        g(x),&x\in B\\
    \end{cases}$$
    is continuous.
\end{lemma}
The lemma also holds if $A$ and $B$ are both open.
\begin{lemma}{(Maps into products)}
    Let $f:A\to X\times Y$ be given by
    $$f(a)=(f_1(a),f_2(a)).$$
    Then $f$ is continuous if and only if $f_1$ and $f_2$ are continuous.
\end{lemma}
Note that there is no useful criterion for maps out of products.

\section{The Product Topology}
In Section \ref{sec:XtimesY} we defined the topology on $X\times Y$ as the topology generated by products of open sets.
However, when considering arbitrary products there are two ways to proceed. Let $J$ be an arbitrary index set and $X_\alpha$ a topological space for each $\alpha\in J$. Then
\begin{definition}
    The box topology on $\prod_{\alpha\in J}X_\alpha$ is generated by sets of the form
    $$\prod_{\alpha\in J}U_\alpha$$
    where each $U_\alpha$ is open in $X_\alpha$.
\end{definition}

\begin{definition}
    The product topology on $\prod_{\alpha\in J}X_\alpha$ is generated by the subasis of all subsets of the form $\pi_\beta^{-1}(U_\beta), \beta\in J$
    where $\pi_\beta: \prod_{\alpha\in J}X_\alpha\to X_\beta$ is the projection mapping. 
    Therefore a basis for the product topology is the collection of subsets of the form
    $$\prod_{\alpha\in J}V_\alpha$$
    where 
    $$V_\alpha =\begin{cases}
        U_\alpha\text{ open in }X_\alpha,&\alpha\in I\\
        X_\alpha,&\alpha\not\in I
    \end{cases}$$
    for some finite $I\subset J$.
\end{definition}
It follows that these two topologies agree for finite cartesian products but differ for the infinite one.
The product topology is quite important, while the box topology main use is as a counter example.

However there are some properties that hold for both topologies
\begin{enumerate}
    \item If $A_\alpha$ is a subspace of $X_\alpha$ for each $\alpha$ then $\prod A_\alpha$ is a subspace of $\prod X_\alpha$ when both products are given in the same topology.
    \item If each $X_\alpha$ is Hausdorff, then $\prod X_\alpha$ is Hausdorff in either topology.
    \item If $A_\alpha\subset X_\alpha$ for each $\alpha$ then
     $$\prod\overline{A_\alpha}=\overline{\prod A_\alpha}$$
     in either topology.
\end{enumerate}

A property that does not hold for the box topology is this
\begin{theorem}
    Let $\prod X_\alpha$ have the product topology. Let $f:A\to\prod X_\alpha$ be given by 
    $$f(a)=(f_\alpha(a))_{\alpha\in J}.$$
    Then $f$ is continuous if and only if $f_\alpha$ is continuous $\forall\alpha\in J$.    
\end{theorem}
\section{The Metric Topology}


\section{The Quotient Topology}
\begin{definition}
    Let $X$ and $Y$ be topological space and $p:X\to Y$ be a surjective map. 
    The map $p$ is called a \textbf{quotient map} if a subset $U$ of $Y$ is open if and only if $p^{-1}(U)$ is open in $X$.
\end{definition}
We say that a subset $C$ of $X$ is \textbf{saturated} if every set $p^{-1}({y})$ the intersects $C$ is contained in $C$.
So we can also say the $p$ is a quotient map if $p$ is continuous and $p$ maps saturated open sets of $X$ to open sets of $Y$.
We can also go the other way and use a quotient map to define a topology.
\begin{definition}
    If $X$ is a space and $A$ is and if $p:X\to A$ is a surjective map, then there exists exactly one topology on $A$ relative to which $p$ is a quotient map.
    We call this topology the \textbf{quotient topology} induced by $p$.
\end{definition}
\begin{definition}
    Let $X$ be a space and $X^*$ a partition of $X$. Let $p:X\to X^*$ be a the surjective map the carries each point of $X$ to the element of $X^*$ containing it. 
    In the quotient topology induced by $p$, the space $X^*$ is called the \textbf{quotient space} $X$.
\end{definition}
Since $X^*$ defines an equivalence relation on $X$, one can think of $p$ as the map that send each element of $X$ to its equivalence class.
Hence a subset $U$ of $X^*$ is a collection of equivalence classes, and so $U$ is open if the the union of the equivalence classes contained in $U$ is open in $X$.

\newpage
\section{Exercises}
\input{exercises.tex}
    
\end{document}